\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    %linkcolor=blue,
    %filecolor=magenta,
    urlcolor=blue,
}
\urlstyle{same}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf {\Large Md Sharique Eliyas} \\
\indent 4th year UG (Dual Degree) student,Department of Computer Science \& Engg. \\
\indent \textbf {Indian Institute of Technology (ISM) Dhanbad}\\
\indent Mobile No. : \textbf{+91-9027962148} \\
\indent Email-id : \textbf{md.sharique.eliyas@gmail.com} \\
\indent Homepage : \textbf{\url{http://shaeli1996.github.io}} \\
\indent Skype id : \textbf{mdsharique.eliyas} \\

\resheading{\textbf{CAREER OBJECTIVE} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.3in} l @{\hskip 0.3in} l @{\hskip 0.3in} l}
To be a part of Organization that provides an atmosphere of mutual growth and benefits, where I can show my\\
talent and potential \\
[-0.6cm]
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{ACADEMIC PROFILE} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
[0.2cm]
\indent \begin{tabular}{ l @{\hskip 0.3in} l @{\hskip 0.3in} l @{\hskip 0.3in} l}
\hline
\textbf{Examination} & \textbf{Institute} & \textbf{Year} & \textbf{CPI/\%} \\
\hline
\\
Dual Degree (Bachelor \& Master & Department of Computer Science \& Engineering & 2014 - & 8.72/10 \\
of Technology) & Indian Institute of Technology(ISM) Dhanbad & 2019\\
\\
Intermediate(+2) & Bihar State Examination Board(BSEB) & 2013 & 76.6 \\
\\
Matricualtion & Bihar State Examination Board(BSEB) & 2011 & 78.4 \\
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Algorithm,Data Structure, Machine Learning, Web Development
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Programming Languages :- } C, C++ Familiar with Python,Java
\item \textbf{Database :- } MySQL
\item \textbf{Platform :- } Windows 8,8.1,10, Linux (ubuntu)
\item \textbf{Machine Learning :- } Numpy, Anaconda, Jupyter Notebook, Pandas
\item \textbf{Web & App Development :- } HTML5, XML, CSS, CSS3, PHP, JavaScript, Codeigniter, Bootstrap
\item \textbf{Tools :- } Matlab,Eclipse, MS Office, Latex, Sublime Text, Adobe Photoshop CS6
\end{itemize}

\resheading{\textbf{KEY ACADEMIC PROJECTS} }\\[\lsep]
\begin{itemize}
\item \textbf{Exchange Rates Forecasting} (Mentor : Prof. P. K. Jana, Dept. of Computer Science 
\& Engg.)\\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Exchange rates forecasting using Radial Basis Function Neural Network.
	\item Improvement in accuracy by ensembling RBF in multistages.
	\item Github Link : \url{https://github.com/shaeli1996}
	\end{itemize}
\item \textbf{Store Sales Forecasting} (Mentor : Prof. P. K. Jana, Dept. of Computer Science 
\& Engg.)\\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Problem Statement and Data Set from \url{https://www.kaggle.com/c/walmart-recruiting-store-sales-forecasting}
	\item Use of Statistical model like Auto Regressive Integrated Moving Average Model for Time Series
	Analysis
	\item Comparison of results from linear regression, KNN regression, Neural Network, LSTM model.
	\item Bagging of different models to get best accuracy.
	\item Github Link : \url{https://github.com/shaeli1996/Store-Sales-Forecasting}
	\end{itemize}
\item \textbf{Collaborative Mobile Charing for Sensor Networks
} (Mentor:Prof. P. K. Jana, Dept. of Computer Science \& Engg.) \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item To determine the path through which mobile charging vehicle will move to assure that every sensore does not run out of energy.
	\item Implementation using Travelling Sales Man problem algorithm.
	\item Improving it for mobile chargin along with Data collection from sensors.
	\item Github Link : \url{https://github.com/shaeli1996}
	\end{itemize}
	\item \textbf{Student/Employee Password Administration Module for MIS} (Mentor : Dr. Chiranjeev Kumar, Dept. of Computer Science \& Engg.) \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Understanding the concept of MVC (Model,View,Control) in CodeIgniter.
	\item Development of Model,View, Control code for given module.
	\item Adding features for special cases like no. of times password can be change, and storing IP address during password change.
	\item Github Link : \url{https://github.com/shaeli1996}
	\end{itemize}
	\item \textbf{Java GUI project}(Mentor : Prof. P. K. Jana, Dept. of Computer Science \& Engg.)
	\begin{itemize} \itemsep \isep
	\item Graphical representation of basic problems like Magic Square, Convex Polygon, Shortest path between two nodes in binary tree etc. using Java GUI and applet.
	\item Github Link : \url{https://github.com/shaeli1996}
	\end{itemize}
\end{itemize}

\resheading{\textbf{SCHOLASTIC ACHIEVEMENTS \& CERTIFICATIONS} }\\[\lsep]
\begin{itemize}
\item \noindent Amongst the top 1\% in JEE Advance 2014 exam with \textbf{CML AIR-5932}
\item \noindent Became in top 0.1\% of Higher Secondary Board Exams among all candidates.
\item \noindent Ranked \textbf{CML AIR 7996} in JEE Main 2014 out of 12 lakh aspirants approximately.
\item \noindent Ranked $48^{th}$ in Bihar Combined Entrance Competitive Examination 2014 (BCECE).
\item \noindent Achieved “B” certificate in National Cadet Corps (N.C.C).
\item \noindent Certification in \textbf{Machine Learning by Andrew Ng} course by Coursera.
\end{itemize}

\resheading{\textbf{COMPETITIVE CODING SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent Solved more than 114 questions on Codechef. (\url{https://www.codechef.com/users/shaeli}).
\item \noindent Won 5 Silver and 6 Bronze medals on HackerRank.(\url{https://www.hackerrank.com/shaeli}).
\item \noindent Solved 153 questions on SPOJ with world rank of 3343(8.3 points) (\url{http://www.spoj.com/users/mdsharique/}).
\item \noindent Actively solves various Machine Learning problems on Kaggle.(\url{https://www.kaggle.com/shaeli})
\item \noindent Secured $32^{nd}$ rank world wide out of 6200 coders in October Circuit'17 on HackerEarth.(\url{https://www.hackerearth.com/challenge/competitive/october-circuits-17/leaderboard/})
\item \noindent Received $\$5 Reward$ in SRM 724 on topcoder. \url{https://www.topcoder.com/members/mdshariqueeliya/}
\item \noindent Secured  $25^{th}$ rank in CodeMarathon , an annual coding contest organised by CSE Society,\\
IIT(ISM) Dhanbad.
\end{itemize}

\resheading{\textbf{EXTRA CURRICULAR ACTIVITIES} }\\[\lsep]
\begin{itemize}
\item \noindent Co-ordinator of Web \& Design Team Hackfest'18,An annual Hackfest of IIT(ISM), Dhanbad.
\item \noindent Dedicated member of KARTAVYA, an NGO that promotes education of the slum children, involved in its academic team as a class teacher.
\item \noindent Designed and coded my own Homepage. Link : \url{https://shaeli1996.github.io}
\item \noindent Served Nation as Batallion in Nation Cadet Corps for 2 Years.

\end{itemize}

\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Competitive Coding, Web surfing
\item \noindent Cycling,Swimming

\end{itemize}
\end{document}

